### 2014-11-10 docs/ms.Rmd
Wrote some really crappy concluding paragraph...I mean really crappy

```{r, barplot, eval = TRUE, echo = FALSE, fig.ext = "pdf", fig.cap = "Figure 1"}

par(mfrow=c(1,2))
props   <- c(specModel, camModel, specLight, CamLight, drk_std, white_stdspec, specAVG, camAVG)
N_props <- c((specs+both), (cam+both), length(DatSpec$light_source), length(DatCam$light_source), length(DatSpec$dark_std), length(DatSpec$white_stdspec), length(DatSpec$specpix_avg), length(DatCam$specpix_avg))

names   <- c("Spec", "Cam", "Spec L", "Pix Avg"," Cam L"," Wt Std", "Spec Avg", "Drk Std")
dat     <- t(arrange(data.frame(props, N_props), props, decreasing = TRUE))
colnames(dat) <- names

barplot(dat[1,], ylim = c(0,100), ylab = "Percentage of studies reporting criteria", xlab = "Criteria", col = "gray", space = 0.30, cex.names = 0.72, mgp = c(2.5,0.5,0), cex.axis = 1.2, cex.lab = 1.5) -> bp.out
abline(h = 0, lwd = 2)
text(dat[2,], x = bp.out, y = 98)
text(paste(round(dat[1,], digits = 0), "%", sep = ""), x = bp.out, y = round(dat[1,], digits = 0)*0.5)
mtext("a)", adj = -0.10, padj = -1, cex = 2)

props_analy   <- c(prop_irrad, prop_spvismod, propvis_mod_param, prop_adap, prop_qcatch, prop_bkg, prop_noise)

N_props_analy <- c(length(DatSpec$irrad_type[! is.na(DatSpec$irrad_type)]), length(DatSpec$vis_mod_sp[! is.na(DatSpec$vis_mod_sp)]), length(DatSpec$vis_mod_param[! is.na(DatSpec$vis_mod_param)]), length(DatSpec$vis_mod_adapt[! is.na(DatSpec$vis_mod_adapt)]), length(DatSpec$vis_mod_qcatch[! is.na(DatSpec$vis_mod_qcatch)]), length(DatSpec$vis_mod_bkg[! is.na(DatSpec$vis_mod_bkg)]), length(DatSpec$vis_mod_noise_type[! is.na(DatSpec$vis_mod_noise_type)]))

dat_analy     <- t(arrange(data.frame(props_analy, N_props_analy), props_analy, decreasing = TRUE))

names_analy   <- c("SpRep", "Bkg", "Irrad", "Qcatch","Noise"," ChrAdapt", "ModPara")
colnames(dat_analy) <- names_analy

barplot(dat_analy[1,], ylim = c(0,100), ylab = "Percentage of studies reporting criteria", xlab = "Criteria", col = "gray", space = 0.30, cex.names = 0.72, mgp = c(2.5,0.5,0), cex.axis = 1.2, cex.lab = 1.5) -> bp.out
abline(h = 0, lwd = 2)
text(dat_analy[2,], x = bp.out, y = 98)
text(paste(round(dat_analy[1,], digits = 0), "%", sep = ""), x = bp.out, y = round(dat_analy[1,], digits = 0)*0.5)
mtext("b)", adj = -0.10, padj = -1, cex = 2)

```

>>>>

##Conclusions

Our objective in this paper was not to point to single studies and lay blame, but to highlight an important gap in reporting that can influence the reproducibility of colour research and cross taxa comparisons. We hope our critical evaluation of recent litearture has highlighted a need for more careful reporting of methological reporting of how colour was measured, but also how it was analysed and can guide how research is communicated improving on the transparency and reproducibility of colour-based science. We belive that part of the issue is simply that researchers seldom have clear insight and guidance on what might be important aspects of their analysis and methods to be reported and we hope our paper will help estbalish more uniform reporting guidelines.
